DATA 621 Homework #3

### 2019-10-25 hw3/HW3.Rmd
More work on HW3

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(corrplot)
library(caret)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

```{r}
df <- read.csv('data/crime-training-data_modified.csv')
evaluation <- read.csv("data/crime-evaluation-data_modified.csv")
set.seed(42)
train_index <- createDataPartition(df$target, p = .8, list = FALSE, times = 1)
train <- df[train_index,]
test <- df[-train_index,]
```

@@

```{r}
train %>% 
  cor(., use = "complete.obs") %>%
  corrplot(., method = "color", type = "upper", tl.col = "black", diag = FALSE)
```

The following show the how predictors are distributed between the areas with crime rates higher than the median *blue) and below the median (red).

@@

@@

@@

```{r}
library(FFTrees)
fit <- FFTrees(target ~ ., train, test, main = "Crime Rate", decision.labels = c("Below Median", "Above Median"))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(corrplot)
library(caret)
library(Amelia)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

```{r}
df <- read.csv('data/crime-training-data_modified.csv')
evaluation <- read.csv("data/crime-evaluation-data_modified.csv")
```

@@

### Are There Missing Values?

```{r}
missmap(df, main = "Missing vs Observed Values")
```

It looks like we have a complete data set.  No need to impute values.

### Splitting the Data

```{r}
set.seed(42)
train_index <- createDataPartition(df$target, p = .7, list = FALSE, times = 1)
train <- df[train_index,]
test <- df[-train_index,]
```

### Exploratory Data Analysis

```{r}
train %>% 
  cor(.) %>%
  corrplot(., method = "color", type = "upper", tl.col = "black", diag = FALSE)
```

The following show the how predictors are distributed between the areas with crime rates higher than the median *blue) and below the median (red).  What we are looking for is variables that could split data into two groups.

@@

NOX seems to be the best variable to divide the data into the two groups

@@

Applying occam's razor we will create a baseline that only has one predictor.  Any model will have to out preform this simplest model.

```{r}
baseline <- glm(target ~ nox, family = binomial(link = "logit"), train)
summary(baseline)
test$baseline <- ifelse(predict(baseline, test) < 0.5, 0, 1)
test$baseline2 <- predict(baseline, test)
confusionMatrix(factor(test$baseline), factor(test$target))
```

@@

```{r}
library(FFTrees)

test <- test[names(train)]

fit <- FFTrees(target ~ ., train, test, main = "Crime Rate", decision.labels = c("Below Median", "Above Median"))
